Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Typo
Typos et al.

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.

The intuition behind both procedures is very straightforward. CCT show that a
local second order polynomial captures all of the unmodeled aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through a
residual bootstrap. Throughout this section and the rest of the paper, we will
let $\E^{*}$, $\Pr^{*}$, etc. denote expectations and probabilities taken with
respect to the distribution induced by the bootstrap (which implicitly
conditions on $X_1,\dots,X_n$ and $Y_1,\dots,Y_n$) and let parameters with
$^{*}$ superscripts be the parameter values under the distribution induced by
the bootstrap. Two $*$ superscripts indicate that the parameter or probability
measure corresponds to a secondary bootstrap distribution.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_-(h) &= \{i : -h < X_{i} < 0\}, &
    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in $I_-(h)$ and
  $I_+(h)$ respectively and $m_-(h,1),\dots,m_-(h,M_-(h))$ and
  $m_+(h,1),\dots,m_+(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_-(h)$ and $I_+(h)$ respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
    the observations in $I_-(b)$ and $I_+(b)$:
    \begin{align}
      \label{eq:2}
      \hat g_-(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
      &\hat g_+(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
    \end{align}
    with
    \begin{align*}
      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise.
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce the
    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation*}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation*}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

>>>>

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.

The intuition behind both procedures is straightforward. CCT show that a
local second order polynomial captures the aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through a
residual bootstrap. Throughout this section and the rest of the paper, we will
let $\E^{*}$, $\Pr^{*}$, etc. denote expectations and probabilities taken with
respect to the distribution induced by the bootstrap (which implicitly
conditions on $X_{1},\dots,X_{n}$ and $Y_{1},\dots,Y_{n}$) and let parameters with
$^{*}$ superscripts be the parameter values under the distribution induced by
the bootstrap. Two $*$ superscripts indicate that the parameter or probability
measure corresponds to a secondary bootstrap distribution.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_{-}(h) &= \{i : -h < X_{i} < 0\}, &
    I_{+}(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_{-}(h)$ and $M_{+}(h)$ to be the number of elements in $I_{-}(h)$ and
  $I_{+}(h)$ respectively, and $m_{-}(h,1),\dots,m_{-}(h,M_{-}(h))$ and
  $m_{+}(h,1),\dots,m_{+}(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_{-}(h)$ and $I_{+}(h)$, respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
    the observations in $I_{-}(b)$ and $I_{+}(b)$:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise.
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation*}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation*}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.
